\vspace{1.0cm} \LARGE \bf Revealing the competitive dynamics of influenza viruses through evolutionary cartography \\ or \\ Charting antigenic drift and evolutionary success of seasonal influenza lineages

### 2013-01-17 flux.tex

%%% errortable %%%
\begin{table}[h]
	\centering
	\caption{\textbf{Average absolute prediction error of log$_2$ HI titer for test data across models and datasets.}}
	\label{errortable}	
	\makebox[\textwidth][c]{
	\begin{tabular}{ c c c c c c c c } 
	\hline
	\multicolumn{4}{c}{} 	&	\multicolumn{4}{c}{Test error}  \\
	Model	&	Dimen 	& 	Serum/virus effects 	& Location Prior					& 	A/H3N2	& 	A/H1N1	& 	B/Vic	& 	B/Yam	\\
	\hline		
	1		&	2D 		&	Fixed $\ses$ 			& Flat								&	0.93 	&	0.79 	&	0.80	&	0.93	\\
	2		&	2D 		&	Fixed $\ses$			& $\beta,\virussd,\serumsd$			&	0.91 	&	0.74 	&	0.77	&	0.83	\\	
	3		&	1D 		&	Fixed $\ses$			& $\beta,\virussd,\serumsd$			&	1.07	&	0.92	&	0.94	&	1.08	\\		
	4		&	3D 		&	Fixed $\ses$			& $\beta,\virussd,\serumsd$			&	0.91	&	0.74 	&	0.79	&	0.84	\\
	5		&	4D 		&	Fixed $\ses$			& $\beta,\virussd,\serumsd$			&	0.95	&	0.75 	&	0.81	&	0.86	\\
	6		&	5D 		&	Fixed $\ses$			& $\beta,\virussd,\serumsd$			&	0.99	&	0.76 	&	0.84	&	0.88	\\				
	7		&	2D 		&	Estimated $\ses, \ves$	& $\beta,\virussd,\serumsd$			&	0.77	&	0.71 	&	0.65	&	0.73	\\	
	8		&	2D 		&	Estimated $\ses, \ves$	& $\beta,\virussd,\serumsd,\tree$	&	0.76	&	0.71 	&	0.64	&	0.72	\\		
	\hline
	\end{tabular}	
	}
\end{table}

>>>>

%%% errortable %%%
\begin{table}[h]
	\centering
	\caption{\textbf{Average absolute prediction error of log$_2$ HI titer for test data across models and datasets.}}
	\label{errortable}	
	\makebox[\textwidth][c]{
	\begin{tabular}{ c c c c c c c c } 
	\hline
	\multicolumn{4}{c}{} 	&	\multicolumn{4}{c}{Test error}  \\
	Model	&	Dimen 	& 	Serum/virus effects 	& Location Prior					& 	A/H3N2	& 	A/H1N1	& 	B/Vic	& 	B/Yam	\\
	\hline		
	1		&	2D 		&	Fixed $\ses$ 			& Uninformed						&	0.93 	&	0.78 	&	0.80	&	0.93	\\
	2		&	2D 		&	Fixed $\ses$			& $\beta,\virussd,\serumsd$			&	0.91 	&	0.74 	&	0.77	&	0.83	\\	
	3		&	1D 		&	Fixed $\ses$			& $\beta,\virussd,\serumsd$			&	1.07	&	0.92	&	0.94	&	1.08	\\		
	4		&	3D 		&	Fixed $\ses$			& $\beta,\virussd,\serumsd$			&	0.91	&	0.74 	&	0.79	&	0.84	\\
	5		&	4D 		&	Fixed $\ses$			& $\beta,\virussd,\serumsd$			&	0.95	&	0.75 	&	0.81	&	0.86	\\
	6		&	5D 		&	Fixed $\ses$			& $\beta,\virussd,\serumsd$			&	0.99	&	0.76 	&	0.84	&	0.88	\\				
	7		&	2D 		&	Estimated $\ses, \ves$	& $\beta,\virussd,\serumsd$			&	0.77	&	0.71 	&	0.65	&	0.73	\\	
	8		&	2D 		&	Estimated $\ses, \ves$	& $\beta,\virussd,\serumsd,\tree$	&	0.76	&	0.71 	&	0.64	&	0.72	\\		
	\hline
	\end{tabular}	
	}
\end{table}
